---
title: "AFL Brownlow Prediction Modelling"
output: html_notebook
---

Install dependancies ( Warning this might take a while, try importing first to see if you have the packages already)
```{r}
install.packages("caret", dependencies = c("Depends", "Suggests"))
```

Import Dependancies
```{r}
library(caret)
source("DBDA2E-utilities.R") 
source("MoreUtilities.R")
library(ggplot2)
library(ggpubr)
library(ks)
library(rjags)
library(runjags)
library(benchmarkme)
```

Load in the Raw Stats
```{r}
raw_stats = read.csv("data/raw_stats.csv")
```

Splitting the raw_stats into train and test sets, with 10% test and 90% training data

 ## TODO Split only the last year of data for the test set, and the previous years as the training data. Don't do this random seeded splitting methodlogy.
```{r}
set.seed(3456)
trainIndex <- createDataPartition(raw_stats$Brownlow.Votes, p = .9, list = FALSE, times = 1)
# Write train and test sets to files.
write.csv(raw_stats[ trainIndex,], "data/train_set.csv", row.names=FALSE)
write.csv(raw_stats[-trainIndex,], "data/test_set.csv", row.names=FALSE)
```

#### Analysis of Split
Read train and test sets from files.
```{r}
train <- read.csv("data/train_set.csv")
test <- read.csv("data/test_set.csv")
```


```{r}
histCompare <- function(train, test, title, xlabel, print=TRUE) {
  c1 <- rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue")
  c2 <- rgb(255,192,203, max = 255, alpha = 80, names = "lt.pink")
  train_set <- as.matrix(train)
  test_set <- as.matrix(test)
  b <- min(c(train_set,test_set)) # Set the minimum for the breakpoints
  e <- max(c(train_set,test_set)) # Set the maximum for the breakpoints
  ax <- pretty(b:e, n = 12) # Make a neat vector for the breakpoints
  hgA <- hist(train_set, breaks = ax, plot = FALSE) # Save first histogram data
  hgB <- hist(test_set, breaks = ax, plot = FALSE) # Save 2nd histogram data
  plot(hgA, col = c1, main=title, xlab=xlabel) # Plot 1st histogram using a transparent color
  plot(hgB, col = c2, add = TRUE) # Add 2nd histogram using different color
  # axis(side=1,at=hgA$mids,labels=seq(b,e))
  # axis(side=1,at=hgB$mids,labels=seq(b,e))
  legend("topright", c("Train Set", "Test Set"), col=c(c1, c2), lwd=10)
  if (print) {
    print(table(train_set))
    print(table(test_set))
  }
}
```


##### Comparing the Train set vs the Test set data split via histogram comparison
```{r}
histCompare(train$Disposals, test$Disposals, "Disposals Train vs Test", "Disposals")
```


```{r}
## TODO contains NA values, need to remove them or have them already removed.
histCompare(train$displayName, test$displayName, "Player Name Train vs Test", "Player Name")
```


```{r}
histCompare(train$CarParks, test$CarParks, "Car Parks Train vs Test", "Car Parks")
```


```{r}
histCompare(train$CarParks, test$CarParks, "Car Parks Train vs Test", "Car Parks")
```


```{r}
histCompare(train$PropertyType, test$PropertyType, "Property Type Train vs Test", "Property Type")
```

# Modelling



### JAGS Model


### Run JAGS



### Results


