---
title: "AFL Browne-Low Raw Stats, Analytics, and Pre Processing"
output: html_notebook
---

This R Notebook is responsible for pre processing the AFL stats so that they can be consumed by the JAGS model.

This project was conducted by Thomas Johnstone, Richard, and Luke Mason, with supervision from RMIT Lecturer Dr Haydar Demirhan Bayesian Statistics 2022.


##### Import Packages and source code
These are the necesery packages and code needed to run the following code samples.
```{r}
source("DBDA2E-utilities.R") 
source("MoreUtilities.R")
library(ggplot2)
library(ggpubr)
library(ks)
library(rjags)
library(runjags)
library(benchmarkme)
```


## Load in the Raw Stats
```{r}
raw_stats = read.csv("data/raw_stats.csv")
```

## Exploratory Data Analysis

### Attach the data to memory
Attaching the data to memory allows us to access the keys of the columns without mentioning the dataset, gives us short hand access to the fields.
```{r}
attach(raw_stats)
```

### Peek at the stats
```{r}
head(raw_stats)
```

### A Summary of the stats
```{r}
summary(raw_stats)
```

### Histograms of frequencies
These are the histograms of each stat field for all games over 10 years.

##### Disposal Analysis
```{r}
hist(Disposals, xlab="Disposals", main="Count of Disposals")
```

# TODO Change this A2 stuff into A3 fields
```{r}
hist(Area, xlab="Area(sqrm)", main="Count of Area(sqrm)")
```
```{r}
hist(Bedrooms, xlab="Bedrooms", main="Count of Bedrooms")
```
```{r}
hist(Bathrooms, xlab="Bathrooms",main="Count of Bathrooms")
```
```{r}
hist(CarParks, xlab="Car Parks", main="Count of Car Parks")
```
```{r}
hist(PropertyType, xlab="Property Type", main="Count of Property Types")
```
```{r}

```
```{r}

```


```{r}


# table(price_data)
# Table of counts per unique value.
# table(SalePrice.100K.)
# table(Area)
table(Bedrooms)
table(Bathrooms)
table(CarParks)
table(PropertyType)

library(gridExtra)
library(grid)
table(price_data$PropertyType)
tb <- table(price_data$PropertyType)
df <- data.frame("Houses"=c(tb)[1],"Units"=c(tb)[2]) 
grid.table(df)

# Density function.
plot(kde(SalePrice.100K.), xlab="SalePrice(100K)", main="Density of Sale Pricings Per 100K")
plot(kde(Area), xlab="Area(sqrm)", main="Density of Area(sqrm)")
plot(kde(Bedrooms), xlab="Bedrooms", main="Density of Bedrooms")
plot(kde(Bathrooms), xlab="Bathrooms",main="Density of Bathrooms")
plot(kde(CarParks), xlab="Car Parks", main="Density of Car Parks")
plot(kde(PropertyType), xlab="Property Type", main="Density of Property Type")

# Scatterplot of each independant variable against the dependant variable.
# plot(Area, SalePrice.100K., main="Sale Price(100K) vs Area(sqrm)", pch=5)
# plot(Bedrooms, SalePrice.100K., main="Sale Pric(100K)e vs Bedrooms", pch=5)
# plot(Bathrooms, SalePrice.100K., main="Sale Price(100K) vs Bathrooms", pch=5)
# plot(CarParks, SalePrice.100K., main="Sale Price(100K) vs Car Parks", pch=5)
# plot(PropertyType, SalePrice.100K., main="Sale Price(100K) vs Property Type", pch=5)

library(car)
scatterplot(SalePrice.100K. ~ Area,         data=price_data, xlab="Area",          ylab="Sale Price (100K)", main="Sale Price(100K) vs Area(sqrm)")
scatterplot(SalePrice.100K. ~ Bedrooms,     data=price_data, xlab="Bedrooms",      ylab="Sale Price (100K)", main="Sale Price(100K)e vs Bedrooms")
scatterplot(SalePrice.100K. ~ Bathrooms,    data=price_data, xlab="Bathrooms",     ylab="Sale Price (100K)", main="Sale Price(100K) vs Bathrooms")
scatterplot(SalePrice.100K. ~ CarParks,     data=price_data, xlab="Car Parks",     ylab="Sale Price (100K)", main="Sale Price(100K) vs Car Parks")
# scatterplot(SalePrice.100K. ~ PropertyType, data=price_data, xlab="Property Type", ylab="Sale Price (100K)", main="Sale Price(100K) vs Property Type")

```
