---
title: "AFL Browne-Low Raw Stats, Analytics, and Pre Processing"
output: html_notebook
---
This project was conducted by Thomas Johnstone, Richard, and Luke Mason, with supervision from RMIT Lecturer Dr Haydar Demirhan Bayesian Statistics 2022.


This R Notebook is responsible for pre processing the AFL stats so that they can be consumed by the JAGS model.




##### Import Packages and source code
These are the necesery packages and code needed to run the following code samples.
```{r}
source("../../utilities/DBDA2E-utilities.R") 
source("../../utilities/MoreUtilities.R")
library(ggplot2)
library(ggpubr)
library(ks)
library(rjags)
library(runjags)
library(benchmarkme)
```


## Load in the Raw Stats
```{r}
raw_stats = read.csv("../../data/raw_stats.csv")
```




```{r}
# Sort by playerid first, then by round, so players are grouped together first, then their rounds they played over the years they played for that round.
attach(raw_stats)
sorted_raw_stats = raw_stats[order(playerId, round),]
sorted_raw_stats
```
Create the list of round names
```{r}
rounds <- c()
for (num in 1:21) {
  rounds <- c(rounds, paste("R", num, sep=""))
}
rounds
```

# Richard's attempt
```{r}
```

# Lukes current attempt at aggregating each players stats for each round from every year
```{r}
# Get the row indices of the playerid
i <- 0
all_indices_ranges <- c()

current_indicies

# Initial id is id of the first row.
currentId <- sorted_raw_stats$playerId[1]
for (row in 1:nrow(raw_stats)) {
    id <- raw_stats[row, "playerId"]
    
    # If new player or end of the list, collect the data and add row to new table (dataframe).
    if (currentId != id) {
      # Aggregate the row ???
      
      
      # Add row to dataframe representing that player aggregated ??
      
      currentId <- id
      current_df = c()
    }
    
    # For every field aggregate the stats
    for (col_num in 1:ncol(raw_stats)) {
      
      # For each round aggregate the field statistics.
      for(round in rounds) {
        
      }
      
    }
    
}
 
# For each field

# Average over the years

raw_stats
```













